%-------------------------
% Resume in LaTeX
% Author: Muhammad Saad
% Based on: Jake Gutierrez's LaTeX Resume Template
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome5}

\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.1pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\sffamily\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Muhammad Saad Ibrahim} \\
    \vspace{6pt}
    {\textbf{\LARGE Software Engineer}} \\
    \vspace{4pt}
    \small
    \faPhone~+201156996498 $|$ 
    \faLinkedin~\href{https://linkedin.com/in/muhammad-saad-ibrahim}{linkedin.com/in/muhammad-saad-ibrahim} $|$
    \faGithub~\href{https://github.com/MuhammadSaadd}{github.com/MuhammadSaadd}\\
    \faHome~Alexandria, Egypt $|$ \faEnvelope~\href{mailto:mu7ammadsa3dd@gmail.com}{mu7ammadsa3dd@gmail.com}
\end{center}

%-----------PROFILE-----------
\section{Profile}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        Experienced Software Engineer specializing in event-driven architectures, event sourcing, and CQRS patterns. 
        Proficient in full-stack development with expertise in TypeScript, F\#, and modern frontend frameworks. 
        Passionate about Clean Architecture, Domain-Driven Design, and building scalable distributed systems.
    }}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Kafrelsheikh University}{Egypt}
      {Bachelor's Degree in Computer Science – Information Systems Department, CGPA: 2.95}{\textcolor{gray}{Aug 2020 -- June 2024}}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textcolor{gray}{Jul 2025 -- Present}}
      {@Bytes Maestros}{Stockholm County, Sweden (Remote)}
      \resumeItemListStart
        \resumeItem{Developed an e-commerce platform from scratch using TypeScript and SvelteKit with Clean Architecture and Domain-Driven Design, implementing event-driven microservices.}
        \resumeItem{Built event-sourced systems using NATS JetStream and PostgreSQL event stores with CQRS pattern, implementing event consumers for order management, product catalog, and marketing features.}
        \resumeItem{Developed SvelteKit frontends with TailwindCSS, Storybook component library, and comprehensive testing (Vitest, Playwright), including internationalization support.}
        \resumeItem{Built a B2B SaaS restaurant management system using F\# and .NET 10 with Oxpecker web framework, applying Functional Core Imperative Shell pattern and schema-first API design with JSON Schema TypeProviders.}
        \resumeItem{Designed and implemented PostgreSQL databases with Kysely query builder, type-safe migrations, optimistic concurrency control, and multi-tenancy support.}
        \resumeItem{Implemented observability-first architecture with causation/correlation IDs for distributed tracing, type-safe validation using Zod and functional programming patterns.}
      \resumeItemListEnd

    \resumeSubheading
      {Backend Developer}{\textcolor{gray}{Nov 2024 -- Jun 2025}}
      {@Techno Island, Software House}{Maadi, Cairo}
      \resumeItemListStart
        \resumeItem{Developed 3 modules from scratch for the \emph{E-Clinic} SaaS application.}
        \resumeItem{Developed 6 modules from scratch for the \emph{NewLoanz} third-party banking CRM system.}
        \resumeItem{Worked on the Transactions Allocation background job and managed the Promises to Pay workflow.}
        \resumeItem{Integrated the \emph{NewLoanz} API with internal and external jobs to process CSV files from the Core Banking System (CBS).}
        \resumeItem{Integrated an online API to retrieve daily currency exchange rates.}
        \resumeItem{Analyzed user stories, BRD documents, and Figma designs to gather requirements.}
      \resumeItemListEnd

    \resumeSubheading
      {Backend Developer}{\textcolor{gray}{Feb 2023 -- Aug 2024}}
      {@Zellige, Product-Based Startup}{Alexandria, Egypt}
      \resumeItemListStart
        \resumeItem{Designed and developed over 45 features, delivering them to customers.}
        \resumeItem{Refactored and optimized the existing codebase, resolving bugs efficiently.}
        \resumeItem{Conducted end-to-end testing with front-end developers to ensure a seamless user experience.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{Custom Shell} $|$ \emph{Codecrafters Challenge} 
        \href{https://github.com/MuhammadSaadd/codecrafters-shell-csharp/tree/master}{\faGithub}}{\textcolor{gray}{May 2025}}
        \resumeItemListStart
          \resumeItem{Developed a custom shell in C\# as part of the Codecrafters challenge.}
          \resumeItem{Implemented core built-in commands (echo, pwd, exit, type) and support for external commands via environment variables.}
          \resumeItem{Enabled directory navigation with \texttt{cd} and implemented robust quoting (single, double, and escape characters).}
          \resumeItem{Added output/error redirection (including append mode) and advanced command auto-completion.}
          \resumeItem{Built modular components: custom input reader (Tab, Backspace, Enter), state machine tokenizer, token parser, and a unified command executor.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Teams Maker} $|$ \emph{Graduation Project} 
        \href{https://github.com/TeamsMaker-Backend/TeamsMaker}{\faGithub}}{\textcolor{gray}{June 2024}}
        \resumeItemListStart
          \resumeItem{Led a team of nine developers, ensuring smooth collaboration and efficient workflows.}
          \resumeItem{Developed a robust backend with ASP.NET Core, creating over 70 APIs for mobile and web clients.}
          \resumeItem{Designed a comprehensive ERD with 20+ tables, following best practices in database design.}
          \resumeItem{Analyzed client needs to ensure the project met all requirements.}
          \resumeItem{\textit{Technologies: ASP.NET 8 Web APIs, EF Core, Microsoft SQL Server, Docker, Swagger.}}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, F\#, TypeScript, SQL} \\
     \textbf{Frameworks}{: Oxpecker, SvelteKit, ASP.NET Core, .NET 10, Entity Framework Core, Dapper, LINQ } \\
     \textbf{Frontend}{: Svelte, TailwindCSS, Flowbite, Vite, Google Maps API, Storybook} \\
     \textbf{Databases}{: Microsoft SQL Server, PostgreSQL, MongoDB} \\
     \textbf{Event Streaming \& Messaging}{: NATS JetStream, RabbitMQ, MassTransit} \\
     \textbf{ORM/Query Builders}{: Kysely, Entity Framework Core, Dapper, Npgsql.FSharp} \\
     \textbf{Methodologies}{: Clean Architecture, Domain-Driven Design, Event Sourcing, CQRS, Functional Core Imperative Shell, Modular Monolith, OOP, SOLID Principles, RESTful API Design, Schema-First API Design, ERD Design, Event-Driven Architecture, Multi-tenancy} \\
     \textbf{Developer Tools}{: Git, GitHub, Docker, Docker Compose, Azure Boards, Rider, pnpm, Moon Build System} \\
     \textbf{Testing}{: Expecto, Faqt, XUnit} \\
     \textbf{Libraries \& Tools}{: Hangfire, FluentResults, Zod, Serilog, Sentry, Better Auth, Inlang/Paraglide}
    }}
\end{itemize}

%-----------CERTIFICATES-----------
\section{Certificates}
\resumeItemListStart
    \resumeItem{ACM ECPC Contest: Qualified for the ECPC Finals in the 2023 season after securing second place in the university qualification round.}
\resumeItemListEnd

\end{document}
